Predicting Spotify Audio Features from Last.fm Tags

### 2023-06-03 paper/main.tex
fixes
more fixes

@@

@@

      Bayes     & 1000 tokens D                       & 0.201            & 0.315           & 0.249          & 0.248           & 0.399          \\

@@

      Tree      & 1000 tags                           & 0.149            &\textbf{0.249}   & 0.184          & 0.236           & 0.291          \\
      Tree      & 10000 tags                          &\textbf{0.148}    & 0.250           &\textbf{0.181}  & 0.235           &\textbf{0.290}  \\

@@

      Tree      & 1000 tokens D                       & 0.173            & 0.278           & 0.215          & \textbf{0.220}  & 0.339          \\

@@

      Tree      & 1000 tokens TC                      & 0.174            & 0.282           & 0.215          & \textbf{0.220}  & 0.344          \\

@@

The Spotify feature that the models had less trouble estimating was the danceability.
The instrumentalness, however, was the feature that presented the highest deviations.
The GTP-2 model was the best model to predict the danceability, with a \num{0.145} RMSE.
The Boosted tree was the best model to predict the instrumentalness, with a RMSE value of \num{0.29}.

In general, the three models performed similarly, with GPT-2 achieving the slightly better results in danceability and acousticness. The Boosted Tree regressor was the best model to predict energy, valence, and instrumentalness.

@@

The Bayesian regressor was a bit more sensitive to changes in tag formating.
This model tended to work better with data formatted by using the Tag Count stringification method.
The Boosted Tree regressor presented less sensitivity to format changes, although the model generally performed better with the Tags as columns format too.

>>>>

\textcolor{red}{what is the limit on the sequence length here?}

@@

      Bayes     & 1000 tokens D                       & 0.201            & 0.315           & 0.249          & 0.297           & 0.399          \\

@@

@@

      Tree      & 1000 tags                           & 0.149            &\textbf{0.249}   & 0.184          & 0.236           & 0.292          \\
      Tree      & 10000 tags                          &\textbf{0.148}    & 0.250           &\textbf{0.181}  & \textbf{0.235}  &\textbf{0.291}  \\

@@

      Tree      & 1000 tokens D                       & 0.173            & 0.278           & 0.215          & 0.268           & 0.339          \\

@@

      Tree      & 1000 tokens TC                      & 0.174            & 0.282           & 0.215          & 0.268           & 0.344          \\

@@

The Spotify feature that the models had less trouble estimating was the danceability, and the energy.
The instrumentalness, however, was the feature that presented the highest deviations.
Acousticness and valence also presented high RMSE values.

The GTP-2 model was the best model to predict the danceability, with a \num{0.145} RMSE.
The Boosted tree was the best model to predict the instrumentalness, with a RMSE value of \num{0.29}.

In general, the three models performed similarly, with GPT-2 achieving slightly better results in danceability, acousticness, and valence.
The Boosted Tree regressor was the best model to predict energy, and instrumentalness.

@@

The Bayesian regressor was a bit more sensitive to changes in tag formatting.
This model tended to work better with data formatted by using the Tag Count stringification method.
The Boosted Tree regressor presented less sensitivity to format changes, although the model generally performed better with the Tags as columns format too.
